---
title: "Data Cleaning"
author: "Kennedy Zapalac"
date: "2023-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
# install.packages("janitor")
library(janitor) # used to clean the column names
```


```{r load data, include=FALSE}
df <- read.csv('LP_Dictator.csv', na.strings=c("", " "))
```
After cleaning the data, here is what it looks like:
```{r clean data, echo=FALSE}
# could keep the page submit buttons to see how long someone thought about something
df <- df %>% 
  # reformat variable names
  clean_names() %>% 
  rename('startDate'='v8', 'endDate'='v9', 'finished'='v10', 'consent'='q44', 'att_check2'='lp_scale_2_6', 'includeOrExclude'='q50') %>% 
  
  # Remove survey metadata, blank surveys, and survey with improper responses
  select(-(v2:v7), -q1, -(q45_1:q2), -(disc_time_1:disc_time_4), -(learn_time_1:learn_time_4), -(perf_time_1:perf_time_4), -(q18_1:q18_4), -(q21_1:q21_4), -(note_time_1:note_time_4),
         -(dg_time_1:dg_time_4), -(q31_1:q31_4), -(q34_1:q34_4), -q24, -q46) %>% # remove metadata columns
  filter(consent == 1) %>%  # remove people who decided not to participate , also removes the extra header
  filter(startDate != "5/22/13 10:06", startDate!= "5/23/13 22:29") %>%   # remove bad survey response (gave the same response to every question, except for the free response where they responded with "f")
  # REMOVE SURVEYS WHERE PEOPLE DIDN'T ANSWER THE FIRST QUESTION
  
  # unencoding some responses and converting to factor so they are easier to use
  mutate(gender = case_when(gender == "1" ~ "male", gender == 2 ~ "female")) %>% # explicitly code gender
  mutate(gender = factor(gender)) %>% # then convert to factor to make it easier to work with in model
  mutate(includeOrExclude = case_when(includeOrExclude == "1" ~ "exclude", includeOrExclude == "2" ~ "include")) %>%# explicitly code include or exclude
  mutate(includeOrExclude = factor(includeOrExclude)) %>% # convert to factor
  
  # create columns indicating participant's condition
  mutate(priming_received = case_when(q10 == "1" ~ "learning", q13 == "1" ~ "performance")) %>% # create column indicating priming received
  select(-q10, -q13) %>% # remove separate columns that used to indicate which priming was received
  mutate(inOrOut = case_when(q17 == "1" ~ "in", q20 == "1" ~ "out", q38 == "1" ~ "in", q41 == "1" ~ "out")) %>% # indicate in or out-group condition
  select(-(q16:q42_4)) %>%  # remove the separate columns used to indicate in or out-group
  # singular column indicating participants condition
  mutate(condition = case_when(priming_received == "learning" & inOrOut == "in" ~ "learn_in",
                               priming_received == "learning" & inOrOut == "out" ~ "learn_out",
                               priming_received == "performance" & inOrOut == "in" ~ "perf_in",
                               priming_received == "performance" & inOrOut == "out" ~ "learn_out")) %>%
  # combine priming responses into one column
  mutate(priming_response = case_when(priming_received == "learning" ~ learn, priming_received == "performance" ~ perform)) %>% 
  
  # indicate if someone passed the second attention check with a 1 and 0 otherwise
  mutate(att_check2 = ifelse(att_check2 == "6", 1, 0)) %>% 
  
  # clean dictator game free response
  mutate(dg = as.numeric(gsub("\\D", "", dg))) %>% # remove extra text, just have numbers
  mutate(dg = case_when(dg == 125 ~ 25, .default = dg)) %>%  # remove typo, was likely supposed to be 25 since that's the max possible value
  
  # convert data types as needed
  mutate_at(c("pt_1", "pt_2", "pt_3", "pt_4", "pt_5"), as.numeric) %>% # convert to numeric to calculate the mean
  mutate_at(c("lp_scale_1_3", "lp_scale_1_4", "lp_scale_1_5", "lp_scale_1_8", "lp_scale_1_9", "lp_scale_2_2", "lp_scale_2_5", "lp_scale_2_8",
              "lp_scale_1_1", "lp_scale_1_2", "lp_scale_1_6", "lp_scale_1_7", "lp_scale_2_1", "lp_scale_2_3", "lp_scale_2_4", "lp_scale_2_7"),
            as.numeric) %>% 
  
  # calculate average scores on scales with multiple items
  # have to reverse code some items first
  # reverse coding for perspective taking
   mutate(pt_1_reversed = case_when(pt_1 == "7" ~ 1, pt_1 == "6" ~ 2, pt_1 == "5" ~ 3, pt_1 == "4" ~ 4, pt_1 == "3" ~ 5, pt_1 == "2" ~ 6, pt_1 == "1" ~ 7),
              pt_3_reversed = case_when(pt_3 == "7" ~ 1, pt_3 == "6" ~ 2, pt_3 == "5" ~ 3, pt_3 == "4" ~ 4, pt_3 == "3" ~ 5, pt_3 == "2" ~ 6, pt_3 == "1" ~ 7),
              pt_5_reversed = case_when(pt_5 == "7" ~ 1, pt_5 == "6" ~ 2, pt_5 == "5" ~ 3, pt_5 == "4" ~ 4, pt_5 == "3" ~ 5, pt_5 == "2" ~ 6, pt_5 == "1" ~ 7)) %>% 
  # avg for PT
  mutate(PT_avg = rowMeans(select(., c("pt_1_reversed", "pt_2", "pt_3_reversed", "pt_4", "pt_5_reversed")), na.rm=T)) %>% 
  # avg for trait-level learning orientation
  # note: someone will still have an average if they're missing an answer, but the NA won't be included in the denominator
  mutate(trait_learning_avg = rowMeans(select(., c("lp_scale_1_3", "lp_scale_1_4", "lp_scale_1_5", "lp_scale_1_8", "lp_scale_1_9", "lp_scale_2_2", "lp_scale_2_5", "lp_scale_2_8")), na.rm=T)) %>% 
  # avg for trait-level learning orientation
  # same note as above
  mutate(trait_performance_avg = rowMeans(select(., c("lp_scale_1_1", "lp_scale_1_2", "lp_scale_1_6", "lp_scale_1_7", "lp_scale_2_1", "lp_scale_2_3", "lp_scale_2_4", "lp_scale_2_7")), na.rm=T)) %>% 
  
  # reorder columns
  select(startDate:self_disc, priming_response, att_check:condition, pt_1_reversed:trait_performance_avg)

# clean letter of support text and extract sentiment
  
  
# preview the cleaned dataset
glimpse(df)
```

## Dealing with missing data
```{r missing data}
# report amount of data
num_columns <- ncol(df)
num_rows <- nrow(df)
# determine missing data for each participant
df$na_counts <- rowSums(is.na(df))
# output number of participants with significant missing data
num_participants_removed <- sum(df$na_counts >= 32)
# remove participants with substantial amounts of missing data
removed_participants <- df %>% filter(na_counts >= 32)
df <- df %>% filter(na_counts < 32)
max_missing <- max(df$na_counts) # report the maximum number of missing responses now
df <- df %>% select(-na_counts, -finished, -consent) # no longer need na counts. 
# Also don't need the finished or consent columns. Anyone who took the survey consented, and finished doesn't seem to actually indicate if someone finished the survey

remaining_participants <- nrow(df) # report the remaining participants

# save the cleaned dataset
write.csv(df, 'LP_dictator_cleaned.csv', row.names=F)
```
There are `r num_columns` columns in our dataset after cleaning. Although there are `r num_rows` rows with each
row representing 1 participant's survey responses, many of these rows have lots of 
missing data. Therefore, I removed `r num_participants_removed` participants data
because they didn't answer any of the questions we used for analysis. After this,
`r remaining_participants` participants remained. Most of them had no missing data,
but there was 1 person with 1 missing response and another with 2 missing responses.

```{r removed participant characeristics}
ggplot(removed_participants, aes(x=age)) + geom_bar() + 
  scale_y_continuous(breaks = seq(0,9,1)) + 
  ggtitle('Age of participants') +
  theme(plot.title = element_text(hjust = 0.5))
print('Summary statistics for the age of removed participants:')
summary(as.numeric(removed_participants$age))
print("For comparisons' sake, here are the summary statistics for the age of the included participants:")
summary(as.numeric(df$age))
print('Gender of removed participants:')
table(removed_participants$gender)
print('Gender of remaining participants:')
table(df$gender)
```
There is no clear reason why these people didn't finish the survey based on the
little data we have about their age and gender. People across the age range dropped
out and both males and females were about equally likely to drop out (about 41%
of the females and 43% of the males didn't complete the survey).

## Conditions
Here is a summary of our sample and how many people we had per condition
```{r conditions, echo=FALSE}
# learning vs performance
knitr::kable(table(df$priming_received))
# in or out
knitr::kable(table(df$inOrOut))
# condition
knitr::kable(table(df$inOrOut, df$priming_received))
# gender tables
knitr::kable(table(df$gender))
knitr::kable(table(df$gender, df$priming_received))
knitr::kable(table(df$gender, df$inOrOut))
```

**Prompt received for learning priming:**

Please think of a time when you met someone new in a social situation. This should be a time when you aimed to understand that person's values, attitudes or background. Please describe the situation in about 1-2 paragraphs. Also, please explain how attempting to learn about a stranger helped you extend your mastery of social situations.

**Prompt received for performance priming:**

Please think of a time when you met someone new in a social situation. This should be a time when you wanted to be judged favorably by that person. Please describe the situation in about 1-2 paragraphs. Also, please explain how conveying that you are likeable to a stranger helped you perform well in the social interaction.

**In-group stranger paragraphs:**

- If female: Who am I generally? I'm a 21 year old White woman, curly hair, athletic. I'm a student. I'd like to think I'm pretty nice and hardworking. I don't really know what else I'm supposed to say...I’m supposed to write about something interesting that’s happened to me lately. Well, I don’t know if this is interesting, but the only thing that I can seem to think of is that two days ago my boyfriend and I broke up. We’ve been dating since our junior year in high school and have been really close. It’s been great being at college together. I thought he felt the same way, but I guess that things have changed. Now he wants to date other people. He says that he still cares a lot about me, but he doesn’t want to be tied down to just one person. I’ve been kind of upset. It’s all I think about. My friends all tell me that I’ll meet other guys and all I need is for something good to happen to cheer me up. I guess they’re right, but so far that hasn’t happened.

- If male: Who am I generally? I'm a 21 year old White man, curly hair, athletic. I'm a student. I'd like to think I'm pretty nice and hardworking. I don't really know what else I'm supposed to say...I’m supposed to write about something interesting that’s happened to me lately. Well, I don’t know if this is interesting, but the only thing that I can seem to think of is that two days ago my girlfriend and I broke up. We’ve been dating since our junior year in high school and have been really close. It’s been great being at college together. I thought she felt the same way, but I guess that things have changed. Now she wants to date other people. She says that she still cares a lot about me, but she doesn’t want to be tied down to just one person. I’ve been kind of upset. It’s all I think about. My friends all tell me that I’ll meet other girls and all I need is for something good to happen to cheer me up. I guess they’re right, but so far that hasn’t happened.

**Out-group stranger paragraphs:**

- If female: Who am I generally? I'm a 21 year old Black woman, curly hair, athletic. I'm a student. I'd like to think I'm pretty nice and hardworking. I don't really know what else I'm supposed to say...I’m supposed to write about something interesting that’s happened to me lately. Well, I don’t know if this is interesting, but the only thing that I can seem to think of is that two days ago my boyfriend and I broke up. We’ve been dating since our junior year in high school and have been really close. It’s been great being at college together. I thought he felt the same way, but I guess that things have changed. Now he wants to date other people. He says that he still cares a lot about me, but he doesn’t want to be tied down to just one person. I’ve been kind of upset. It’s all I think about. My friends all tell me that I’ll meet other guys and all I need is for something good to happen to cheer me up. I guess they’re right, but so far that hasn’t happened.

- If male: Who am I generally? I'm a 21 year old Black man, curly hair, athletic. I'm a student. I'd like to think I'm pretty nice and hardworking. I don't really know what else I'm supposed to say...I’m supposed to write about something interesting that’s happened to me lately. Well, I don’t know if this is interesting, but the only thing that I can seem to think of is that two days ago my girlfriend and I broke up. We’ve been dating since our junior year in high school and have been really close. It’s been great being at college together. I thought she felt the same way, but I guess that things have changed. Now she wants to date other people. She says that she still cares a lot about me, but she doesn’t want to be tied down to just one person. I’ve been kind of upset. It’s all I think about. My friends all tell me that I’ll meet other girls and all I need is for something good to happen to cheer me up. I guess they’re right, but so far that hasn’t happened.

## Quality checks
### attention check:
To ensure that people were paying attention, they were asked to describe what they had read. Some people did not answer that question, so they may not have been paying attention
```{r attention check 1, echo=FALSE}
print('How many people answered the first attention check, which asked them to summarize what they read?')
knitr::kable(table(!is.na(df$att_check)))
```
Everyone answered the first attention check, and everyone except for one person gave reasonable answers.
This person was using vulgar language in their responses and was mad that the survey
didn't pay more. I will be removing this person's responses.

```{r attention check 2}
knitr::kable(table(df$att_check2))
```
Almost no one passed the second attention chedck, which asked them to pick a specific
answer to prove they were paying attention. There may be some concerns about the
quality of this data. People may have been paying attention in the beginning of
the survey and faded as it went on. We can't remove people who failed the attention
check since we would have no data left.

### include or exclude:
**Participants read this:** The study is very important to us and a considerable amount of time and effort has gone into creating this survey. As such, if for whatever reason you feel that you did not complete the survey carefully or accurately, it would be extremely helpful if you could let us know this
now. Your response will in no way affect your compensation or reputation on Mturk.

**And then responded with:**

- I  DID NOT complete the survey carefully or accurately. Please exclude my responses from analysis.
- I DID complete the survey carefully or accurately. Please include my responses from analysis.
```{r exclude responses, echo=FALSE}
print('How many people said to include or exclude their responses?')
table(df$includeOrExclude)
```
Should we remove these 2 participants data?

## Textual analysis
**Columns that we could perform textual analysis on and their prompts:**

- `self_disc`: Now we would like to get to know a little bit more about you. Please write one paragraph about who you are generally (keep it anonymous), and please describe something interesting that has happened in your life recently. This paragraph will randomly be shown to future Mturk participants to read.
- `note`: Now you have the opportunity to write a note to the participant you just read about. Please respond with your thoughts and feelings to his/her "interesting thing that has happened". Your message will be emailed to this participant (and he/she will not receive any other information about you).Please write a 1-2 paragraph response below:

```{r textual analysis}

```

## Exploratory Data Analysis
```{r}

```

## Classification Using Logistic Regression
```{r modeling}

```

