---
title: "Can a Learning Orientation Reduce In-Group Bias?"
author: "Kaylee Billstone, Paulina Brown, Jaqueline Marroquin, Christian Ozuna, Kirsten Richards, and Kennedy Zapalac"
date: "2023-10-02"
output: github_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project Overview

**What is in-group bias and why does it matter?**

In-group bias is the preferential treatment of people with whom you share a common identity, such as gender, race, or culture. In-group bias can be harmful when it leads to unfair outcomes, such as when a perfectly qualified job candidate is not hired because of their race. Current research is focused on reducing in-group bias to mitigate its harmful effects.[@wang2015]

**Our aims:**

Along this line, we are investigating if in-group bias can be influenced by priming people with a learning versus performance orientation. A learning orientation is other-focused (trying to get to know another person), whereas as performance orientation is self-focused (trying to make a good impression). Other studies have demonstrated that in-group bias is influenced by the priming received, so we expect the priming our participants received will affect their in-group bias [@bettencourt1997]. Specifically, we will:

1.  Determine how perspective taking, empathetic concern, and altruism is different among in-group versus out-group members. Do our participant's display an in-group bias such that they have an easier time understanding, express more empathy for, and exhibit altruistic behavior toward in-group members?
2.  Determine if the priming received (learning versus performance) influenced perspective taking, empathetic concern, and altruism towards out-group members.

A few other aims we could pursue later:

1.  How does trait-level orientation influence the effectiveness of the priming received in reducing in-group bias?
2.  Investigate whether there are gender-related differences in the effectiveness of the learning orientation prime in reducing in-group bias.
3.  Perform textual analysis on the participants' responses to the person going through a hard time. We could extract additional variables, which could be used to understand in-group bias. For example, can we use the sentiment expressed to predict how empathetic someone rated themselves as? Could we predict if someone had received a learning or performance orientation prime based on their language? Or does someone's trait-level orientation strongly influence their language usage?

**Our dataset:**

Our dataset can be accessed [here](https://github.com/kzapalac/SDS322E_project/blob/main/LP_Dictator.csv). You can also reference the survey outline [here](https://github.com/kzapalac/SDS322E_project/blob/main/LP_Dictator.pdf) to understand the dataset better.

The sample includes white adults who identified as male or female, and the survey was conducted entirely online. Participants were asked to write a paragraph about themselves, and they received a learning or performance prime. Next, they read about a gender-matched in-group or out-group member (e.g., white or black stranger) going through a hard time. Then, the participants wrote a letter of support to this person, filled out a 5-item questionnaire about how easy it was to take the other person's perspective, a 1-item measure about how much empathetic concern they felt for the person, and play a one-shot dictate game. Trait-level learning and performance orientation was also assessed. There were two quality measures, which may reduce the size of the dataset, including an attention check and asking whether or not their responses should be included.

Overall, there are:

-   2 independent variables: in-group/out-group stranger and learning/performance orientation

-   3 dependent variables: perspective taking, empathetic concern, altruism (via dictator game)

-   2 potential covariates: trait level learning/performance orientation, gender

# Exploratory Data Analysis
```{r load data}
library(tidyverse)
df <- read.csv("LP_Dictator_cleaned.csv")
df <- df %>% filter(startDate != "5/22/13 10:06")

# remove text from dg column


# might want to remove attention check and excluded responses

```

### In-Group vs. Out-Group Perspective Taking, Empathetic Concern, and Altruism
```{r}
# Christiana
# graphs for empathy
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_violin()
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_boxplot()
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_bar(stat='summary') +
  geom_errorbar(stat='summary', width = 0.3)

# create summary table with mean, sd, se, and cis
df %>% filter(!is.na(inOrOut)) %>% group_by(inOrOut) %>% summarize(n = n(), mean = mean(emp, na.rm=T), sd = sd(emp, na.rm=T), se = sd/sqrt(n), lower_ci = mean - 1.96*se, upper_ci = mean + 1.96*se)

# test with removing attention check
df %>% filter(!is.na(inOrOut), !is.na(att_check)) 
```
Description of graph:
Hypothesis based on graph:

```{r}
# Kaylee
# remove extra text, just have numbers
df$dg <- as.numeric(gsub("\\D", "", df$dg))
# graphs for altruism (dictator game) 
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_violin()
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_boxplot()
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_bar(stat='summary') +
  geom_errorbar(stat='summary', width = 0.3)

```
Description of graph:
Hypothesis based on graph:

```{r}
# Kennedy
# graphs for perspective taking
# create composite variable (avg of 5 questions)
# make sure to reverse code questions so that a 7 represents better perspective taking
# df %>% mutate(pt_1_reversed = case_when(pt_1 == "7" ~ 1, pt_1 == "6" ~ 2))
# select the correct pt questions (reversed or normal)
# df %>% mutate(PT_avg = rowMeans(select(., c("pt_1_reversed", "pt_2", "", "", ""))), na.rm=T)
```
Description of graph:
Hypothesis based on graph:


### Influence of Priming on Out-Group Perspective Taking, Empathetic Concern, and Altruism

```{r}
# empathy
df %>% filter(!is.na(inOrOut)) %>% ggplot(aes(y=emp, x = inOrOut)) + geom_violin() + facet_wrap(~priming_received)
```
Description of graph:
Hypothesis based on graph:

```{r}
# altruism

```
Description of graph:
Hypothesis based on graph:

```{r}
# perspective taking

```
Description of graph:
Hypothesis based on graph:
# References
